\documentclass[a4paper,nojss]{jss}
\usepackage{amsmath,amssymb,amsfonts,thumbpdf, caption, subcaption, lipsum}
%\usepackage[utf8]{inputenc}

\newcommand{\CRANpkg}[1]{\href{http://CRAN.R-project.org/package=#1}{\pkg{#1}}}%
\newcommand{\samp}[1]{`\code{#1}'}%
\DefineVerbatimEnvironment{example}{Verbatim}{}
\setkeys{Gin}{width=\textwidth}

%% for internal use
\newcommand{\fixme}[1]{\marginpar{\color{black}fixme} {\color{red}#1}}
\newcommand{\readme}[1]{\marginpar{\color{black}readme} {\emph{\color{red}(#1)}}}
\usepackage{chngcntr}

%%% jss stuff
%\let\proglang=\textsf
%\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}
%\bibliographystyle{jss}
%\makeatletter
%\newcommand\code{\bgroup\@makeother\_\@makeother\~\@makeother\$\@codex}
%\def\@codex#1{{\normalfont\ttfamily\hyphenchar\font=-1 #1}\egroup}
%\makeatother

\title{Distributional Trees and Forests for Circular Data}

\author{Moritz N. Lang\\University of Innsbruck 
\And Lisa Schlosser\\University of Innsbruck 
\And Torsten Hothorn\\University of Zurich 
\AND Georg J. Mayr\\University of Innsbruck 
\And Reto Stauffer\\University of Innsbruck 
\And Achim Zeileis\\University of Innsbruck}

\Plainauthor{Moritz N. Lang}

\Abstract{
Circular data can be found in a variety of applications and subject areas,
e.g., hourly crime rates in the social-economics, animal movement direction in
ecology, and wind direction as one of the most important weather variables in
meteorology. For probabilistic modeling of circular data the von Mises
distribution is widely used. While most existing approaches are built on
additive regression models, we propose an adaption of regression trees to
circular data by employing distributional trees. In comparison to the more
commonly-used additive models, the resulting distributional trees are easy to
interpret, can detect non-additive effects, and automatically select covariates
and their interactions. In addition, as a natural extension, ensembles or
forests of such circular trees are introduced that can further improve the
forecasts by regularizing and stabilizing the model. For illustration,
short-term probabilistic wind direction nowcasts at different airports are
obtained in order to direct airplanes to a safe landing. The predictive skill
of the novel approaches is benchmarked with an additive regression model plus a
persistency and a climatology model, employing the circular continuous ranked
probability score. The proposed methods for circular distributional trees and
forests are available in the R package ``disttree'' from R-Forge.
} 

\Keywords{Distributional Trees; Distributional Forest; Circular Response; Von Mises Distribution}

\Address{
  Moritz N. Lang\\
  University of Innsbruck\\
  6020 Innsbruck, Austria\\
  E-mail: \email{moritz.lang@uibk.ac.at}
}

\begin{document}
\end{document}
